Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2021-04-23 paper/ifo-complexAudio.tex
fixing placeholder text in section V, putting authors back in for now (had commented for double blind review)

This analysis is indirectly related to the advanced signal processing techniques required to extract gravitational-wave signals. 
Instead, the apparatus serves as an independent demonstration for a broader physics and engineering audience, particularly in undergraduate laboratories. 
We describe additional hardware components required for this demonstration in Section~\ref{sec:photodiode} and the initial results in Section~\ref{sec:initialResultsOpMic}. 
A selection of filters are applied to the data, details of which are presented in Supplementary Material and we present the results of the best performing filters in Section~\ref{sec:opticalMicResults}. \han{rephrase depending on what we show.}

@@

\begin{figure}
	\includegraphics[width=.45\textwidth]{figures/psd_podo_14_6.pdf}
	\caption{\label{fig:psd_noise}
\han{If we do not cover the butterworth filter in the main text, I'd suggest only showing the top panel of this figure in the main text. We can include the twp panel version in the butterworth section of the supplementary material}
Power spectral density (PSD) of background noise from the optical microphone (with the speaker off). 
% Bottom: the PSD after applying a Butterworth bandpass filter (bottom panel) between the two frequencies marked with red, dashed lines. 
We see strong power from the $50\,{\rm Hz}$ mains hum and its harmonics (most likely from the photodiode circuit and the room’s lighting and cooling). Otherwise, the PSD is fairly white except for a peak at around 0.75~kHz. 
% After filtering we see strong attenuation (at least 3~dB) of all frequencies outside the band, but little change to the harmonics within the band.
}
\end{figure}

>>>>

This analysis is indirectly related to the advanced signal processing techniques required to extract gravitational-wave signals. 
Instead, the apparatus serves as an independent demonstration for a broader physics and engineering audience, particularly in undergraduate laboratories. 
We describe additional hardware components required for this demonstration in Section~\ref{sec:photodiode} and the initial results in Section~\ref{sec:initialResultsOpMic}. 
A selection of filters are applied to the data, details of which are presented in Supplementary Material. 
We present the two best performing analyses from our Supplementary Material in Section~\ref{sec:opticalMicResults}.

@@

\begin{figure}
	\includegraphics[width=.45\textwidth]{figures/psd_podo_14_6.pdf}
	\caption{\label{fig:psd_noise}
Power spectral density (PSD) of background noise from the optical microphone (with the speaker off). 
% Bottom: the PSD after applying a Butterworth bandpass filter (bottom panel) between the two frequencies marked with red, dashed lines. 
We see strong power from the $50\,{\rm Hz}$ mains hum and its harmonics (most likely from the photodiode circuit and the room’s lighting and cooling). Otherwise, the PSD is fairly white except for a peak at around 0.75~kHz. 
% After filtering we see strong attenuation (at least 3~dB) of all frequencies outside the band, but little change to the harmonics within the band.
}
\end{figure}
